% !TEX root = ./ICDE14_conf_full_296.tex
\section{Introduction}

%\marcos{The introduction now reads a bit too generic, and a bit too rich in buzzwords (big data, crowd sourcing). What is the problem that is being addressed?}
%what's the situation

%- why do people need to do cartographic generalization?

%- how do people go about this task today?

%- what is the main related work, and why is it not enough?

%Map generalization has a long tradition spanning hundreds of years, and has rightly been considered as much an art as a science~\cite{rieger1993consensus}.
%\marcos{Not very clear what map generalization really means, now that the examples are completely gone.}
%\marcos{GST?}
%\martin{The new abstract and introduction looks good, but I think that the examples in the old abstract would work well in one of the paragraph below. I would also suggest that "precision" and "legibility" is defined and/or examplified.}

The goal of map generalization is to produce a map at a given scale that achieves the right balance between rendering performance and information quality for end users. For example, in a tourist attraction rating system, one needs to efficiently visualize important attractions, and constrain object proximity to allow space for user interaction. In a journalistic piece that maps traffic incidents, \hl{however,} maintaining the underlying distribution of data is the most important aspect, but at the same time object density must be constrained to ensure high-performance data transfer and rendering.

%A benefit of data reduction in digital maps is that performance can improve vastly be reducing the amount of data that needs to be handled when rendering a portion of the map. In \emph{automated} map generalization the generalization process is performed either entirely or partially by algorithms on a computer.

Fully automatic generalization of digital maps~\cite{sarma2012fusiontables,nutanong2012multiresolution} is relevant in many areas such as social networks, factivism and data journalism~\cite{cohen2011journalism,bono,sankaranarayanan2009twitterstand}, where there is a constant need for visualizing new and often massive geospatial datasets. Automatic generalization includes \hl{both data reduction and graphical rendering}~\cite{weibel1999generalising,gruenreich1985cag}. Increasingly, \hl{graphical rendering is deferred to map clients}. This trend leaves the challenging problem of data reduction, i.e., selecting the right information to be displayed across zoom levels of the map, to the \hl{map service provider}~\cite{gaffuri12vectortiles}. 

Both the performance and quality of a generalized map become important as the map gains a large audience. A map generalization solution handling data reduction in this context should be able to deal with big spatial datasets, consisting of both point and polygon records, should be usable by novice programmers, and should be able to finish processing quickly, e.g., in time for a tight news agency deadline. Ideally, such a system will allow users to control the important aspects of generalization solutions using logical and concise measures and reuse existing technology as much as possible, e.g., relational database technology.

Unfortunately, current approaches for data reduction in map generalization fall short in one or many of the above dimensions. Recent work has mostly considered only explicit rules or pre-set constraints for map generalization, resulting in solutions that are either too \hl{tedious}~\cite{sld,mapnik}, or too restrictive for \hl{users}~\cite{sarma2012fusiontables,nutanong2012multiresolution}. In addition, previous solutions have been poorly integrated with existing technology, resulting in scalability bottlenecks such as being restricted to the main memory capacity of a single node~\cite{sarma2012fusiontables}. 
 

Spatial data is often stored in a database with powerful spatial extensions installed, so a natural idea is to exploit the processing capabilities of the database to perform map generalization. In this work, we present a novel \emph{database-integrated} approach that is a complete solution to the data reduction problem in map generalization. All operations are performed entirely within the database process, and the result is a preprocessing of spatial records for fast execution of subsequent scale-parameterized queries~\cite{hilbert1891ueber}. Essentially, a number is assigned to each spatial record corresponding to the lowest zoom-level at which the record should be visible in a zoomable map, allowing for efficient indexing.

Using a \emph{declarative language}, we allow the user to concisely express spatial constraints and object importance, which are used to compute a multi-scale database from an input table of spatial data. This gives users a large amount of control over the map generalization process, while still being extremely concise, expressing a generalization with as little as four lines of code. 

\hl{We term our approach }\emph{\hl{declarative cartography}}\hl{, since it combines a declarative language for data reduction with a compilation procedure that results in efficient database programs to transform data for cartographic visualization.}

%\marcos{Revise arguments wrt. related work + open-source?}
%\martin{The paragraph below belongs, I think, to the related work section. Alternatively, it can be shortened a bit here and the extended version given in the related work section.}
%
%We know of two recent papers which address the problem of data reduction problem~\cite{nutanong2012multiresolution,sarma2012fusiontables}. While both of these approaches provide good solutions to the data reduction problem with good running time, there are distinct and overlapping shortcomings to both of these which are not suffered by our approach.  Both of these approaches support only fixed constraints, while we allow a large class of constraints to be defined by the user. The first paper~\cite{sarma2012fusiontables} seems to indicate that the dataset must fit main memory and implies that data must be serialized in and out of the database for processing, none of which is true of our system. The other published approach~\cite{nutanong2012multiresolution} seems to require modifications to the database engine, which is not true of our system either. Neither of these previously published systems offer a language interface to users, but do imply a mechanism for parameterizing the fixed constraints. While~\cite{sarma2012fusiontables} show that there is at least mathematical support in their approach for several different objective functions, it is not clear how a user would actually express new objectives in a way that is understood by the system. Finally, users can take our implementation and start running it on their own infrastructure using only free, unmodified, open source software.

\vspace{5em}

In this paper, we make the following four contributions:
\begin{enumerate}
\item We present a declarative language, Cartographic Visualization Language (CVL, pronounced ``civil''), for generalizing spatial datasets. CVL is designed to be simple and concise to use for novice programmers. The CVL language was designed in collaboration with the Danish Geodata Agency and Grontmij in Denmark.\footnote{\url{http://www.gst.dk/English/}}\footnote{\url{http://grontmij.dk/}}

\item We \hl{convert} the data reduction problem in map generalization \hl{to an instance of} the well-known \emph{set multicover problem}~\cite{rajagopalan1998primal}, which makes constraints fully pluggable and allows reuse of well-known algorithms~\cite{rajagopalan1998primal,vazirani2001approximation}.

\item We show how to fully evaluate CVL inside the database; this enables us to reuse basic database technology for data management and scalability. While CVL is designed to compile to a variety of engines~\cite{Stonebraker:2010:PDBMSvsMapReduce}, we present here an implementation using a relational database engine with spatial extensions. The code for the project is available as open source through the project website.\footnote{\url{http://github.com/dmslab/declarativecartography}}

\item We present experimental results for a variety of real datasets. The results show that the proposed approach has good performance and produces high-quality map generalizations.
\end{enumerate}

In Section~\ref{sec:background}, we define the data reduction problem in map generalization as a \hl{selection problem}. In Section~\ref{sec:cvl:language}, we introduce the CVL language. In Section~\ref{sec:optimizationmodel}, we formalize the \hl{selection problem as a combinatorial optimization problem} based on a mapping to the set multicover problem, and we revisit algorithms for this problem in Section~\ref{sec:algorithms}. In Section~\ref{sec:implementation}, we discuss the compilation procedure that enables us to run CVL on a relational database backend. Experimental results are presented in Section~\ref{sec:experimental}, and finally related work is summarized in Section~\ref{sec:related}.
